Data Preparation

### 2019-01-10 Data Preparation.Rmd
debugging import section

# Import Data
The datasets we use are saved as spreadsheet on our google drive *DARS*. We use the function `gsheet2tbl` to import them to `R Studio` as tibbles. We use the tibble data format (an evolution of the data frame format) because this is the format of reference of the `tidyverse` on whose tools our analysis is heavily based.

@@

### Course Manuals
To expand our topic modeling of course content, we would like to analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
```{r corpus_manuals, cache = TRUE}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                         readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```

## Student Data
The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2]. `transcripts` contains information on each course taken by each student such as the receives grade, the semester in which teh course was taken as well as the calendar year.

ALL OTHER STUDENTS:
The data we will be using was provided in two documents with the same format. We import them, merge them and remove duplicate rows.

```{r Data Import}
d_transcript <- rbind(read_csv("Raw Grades/grades1.csv", na.strings=c("","NA")),
                      read_csv("Raw Grades/grades2.csv",na.strings=c("","NA"))) 
d_transcript <- d_transcript[!duplicated(d_transcript),] #could use distinct() from dplyr
```

>>>>

# Import Data
The datasets we use are saved as spreadsheet on our google drive *DARS* (with exeption of grade data saved as csv files on the computer for privacy reasons). We use the function `gsheet2tbl` to import them to `R Studio` as tibbles. We use the tibble data format (an evolution of the data frame format) because this is the format of reference of the `tidyverse` on whose tools our analysis is heavily based.

@@

### Course Manuals
To expand our topic modeling of course content, we would like to analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
```{r}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                         readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data
The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2]. `transcripts` contains information on each course taken by each student such as the receives grade, the semester in which the course was taken as well as the calendar year.

The data we will be using was provided in two documents with the same format. We import them, merge them and remove duplicate rows.

```{r Data Import}

x <- read_csv("Raw Grades/grades1.csv", col_types = cols())
t1 <- read.csv("Raw Grades/grades1.csv",na.strings=c("","NA"))
t2 <- read.csv("Raw Grades/grades2.csv",na.strings=c("","NA"))
d_dirt <-rbind(t1, t2)
d_dirt <- d_dirt[!duplicated(d_dirt),] #could use distinct() from dplyr
```
